API design for machine learning software: experiences from the scikit-learn project

### 2013-09-10 paper.tex
remove OvO example, it's too long

Some machine learning algorithms are expressed naturally
as meta-algorithms parametrized on simpler algorithms.
Examples include ensemble methods which
build and combine several simpler models (e.g., decision trees), or multiclass
and multilabel classification schemes which can be used to turn a binary
classifier into a multiclass or multilabel classifier. In \sklearn, such algorithms are
implemented as \textit{meta-estimators}. They take as input an existing base
estimator and use it internally for learning and making predictions.
All meta-estimators implement the regular estimator interface.

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
A different scheme can be achieved
by a meta-estimator wrapping a logistic regression estimator:
\begin{pythoncode}
from sklearn.multiclass import OneVsOneClassifier

ovo_lr = OneVsOneClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
For learning, the \texttt{OneVsOneClassifier} object
\textit{clones} the logistic regression estimator multiple times,
resulting in a set of $\frac{K(K-1)}{2}$ estimator objects
for $K$-way classification,
all with the same settings.
For predictions, all estimators perform a binary classification and then vote to make the final decision.
The snippet exemplifies the importance
of separating object instantiation and actual learning.

Since meta-estimators require users to construct nested objects,
the decision to implement a meta-estimator
rather than integrate the behavior it implements
into existing estimators classes
is always based on a trade-off between generality and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.

% TODO: show a grid search on this estimator

>>>>

Some machine learning algorithms are expressed naturally
as meta-algorithms parametrized on simpler algorithms.
Examples include ensemble methods which
build and combine several simpler models (boosting, bagging, random forests),
or multiclass classification schemes which combine multiple binary classifiers.
In \sklearn, such algorithms are implemented as \textit{meta-estimators}.
They take as input an existing estimator
and use it internally for learning and making predictions.
All meta-estimators implement the regular estimator interface.
% XXX bagging example here

Since meta-estimators require users to construct nested objects,
the decision to implement a meta-estimator
rather than integrate the behavior it implements
into existing estimators classes
is always based on a trade-off between generality and ease of use.
